### 2022-06-01 Publish Paper/manuscript_main.tex
Update Paper

\subsection{Experiment Setup}
All the model in this paper is trained with Adam Optimizer\cite{6980}. The initial learning rate is set to $0.001$, an learning rate reduction schedule is setup with the minimum learning rate is $0.0000001$ with the factor of $0.2$. Otherwise, the epsilon argument of the optimizer is set to $0.1$. 

>>>>

\subsection{Traning}
Before training, the dataset is split into three sub datasets including training, validation, and testing. In this paper, the graphic card that is used to train is Nvidia RTX TitanV.\\
All the model in this paper is trained with Adam Optimizer\cite{6980}. The initial learning rate is set to $0.001$, an learning rate reduction schedule is setup with the minimum learning rate is $0.0000001$ with the factor of $0.2$, the epsilon argument of the optimizer is set to $0.1$. On the other hand, Early Stopping is also set up, if the accuracy of validation set dose not increase after 25 epochs, the training will stop. 
